### 2021-05-18 sections/queueing_model/main.tex
Place all tikz pictures in imgs\ directory
Apply suggestions from code review
Co-authored-by: Vince Knight <vincent.knight@gmail.com>

% TODO: If this is to be one paper maybe the first two paragraphs do not need to
% include so much details or even better omit some of the details in the game
% overview section.
In this section, a more in-depth explanation of the queueing model shown in 
figure \ref{fig:diagram_of_queueing_system} will be given.
This is a queuing model that consists of two waiting spaces, one for each type
of patient.

@@

\input{sections/queueing_model/general_markov_model/main.tex}

In order to acquire an exact solution of the problem a slight adjustment needs 
to be considered. 
The problem defined above assumes no upper boundary to the number of individuals 
that can wait for service or for the ones that are blocked in the buffer centre. 
Therefore, a different state space \( \tilde S \) needs to be constructed where 
\( \tilde S \subseteq S \) and there is a maximum allowed number of people \(N\) 
that can be in the system and a maximum allowed number of people \(M\) that can
be blocked in the buffer centre:

>>>>

% TODO: If this is to be one paper maybe the first two paragraphs do not need to
% include so much details or even better omit some of the details in the game
% overview section.
In this section, a more in-depth explanation of the queueing model shown in 
figure \ref{fig:diagram_of_queueing_system} will be given.
This is a queuing model that consists of two waiting spaces, one for each type
of individual.

@@

\input{imgs/general_markov_model/main.tex}

In order to consider this model numerically an adjustment needs 
to be made. 
The problem defined above assumes no upper boundary to the number of individuals 
that can wait for service or for the ones that are blocked in the buffer centre. 
Therefore, a different state space \( \tilde S \) needs to be constructed where 
\( \tilde S \subseteq S \) and there is a maximum allowed number of individuals \(N\) 
that can be in the system and a maximum allowed number of individuals \(M\) that can
be blocked in the buffer centre:

### 2021-05-18 sections/queueing_model/subsections/performance_measures/main.tex
Write main.tex for waiting time subsubsection
Add python code that generates tikz picture
In order for the code to work, ambulance_game needs
to be imported first.
Comment out section
Include section that was commented out
Minor change on input
Apply suggestions from code review
Co-authored-by: Vince Knight <vincent.knight@gmail.com>

The transition matrix \( Q \) defined in \ref{eq:markov_transition_rate} can be 
used to get the probability vector \( \pi \).
The vector \( \pi \) is commonly used to study stochastic systems and it's main
purpose is to keep track of the probability of being at any given state of 
the system.
The term \textit{steady state} refers to the instance of the vector \( \pi \) 
where the probabilities of being at any state become stable over time. 
Thus, by considering the steady state vector \( \pi \) the relationship between 
it and \( Q \) is given by:

@@

>>>>

The transition matrix \( Q \) defined in \ref{eq:markov_transition_rate} can be 
used to get the probability vector \( \pi \).
The vector \( \pi \) is commonly used to study stochastic systems and it's main
purpose is to keep track of the probability of being at any given state of 
the system. \(\pi_i\) is the steady state probability of being in state \((u_i, v_i)\in\tilde S\) which is the \(i\)th state of \(tilde S\) for some ordering of \(\tilde S\).
The term \textit{steady state} refers to the instance of the vector \( \pi \) 
where the probabilities of being at any state become stable over time. 
Thus, by considering the steady state vector \( \pi \) the relationship between 
it and \( Q \) is given by:

@@

\input{sections/queueing_model/subsections/performance_measures/waiting_time/main.tex}

\input{sections/queueing_model/subsections/performance_measures/blocking_time/main.tex}

\input{sections/queueing_model/subsections/performance_measures/proportion_within_target/main.tex}
